---
title: HW 2
author: Haley Uyeunten
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(gapminder)
library(nycflights13)
```

# Activity 1
```{r}
data <- c(-1, 0, 4, 15)
root_data <- sqrt(data)
root_data
```
R gives a warning that the square root of a negative number is not a number.

# Activity 2
```{r}
data(txhousing)
glimpse(txhousing)
```
The data set contains 8,602 observations and 9 variables. The variables are
city (character), year (int), month (int), sales (double), volume (double),
median (double), listings (double), inventory (double), and date (double). 

# Activity 3
```{r}
data(gapminder)
p <- ggplot(data = gapminder, mapping = aes(x = pop, y = gdpPercap))
p + geom_point()
```

There could be strands of data points because there are many countries with
similar GDPs but different populations, and many countries with similar
populations but different GDPs.

# Activity 4
```{r}
delta <- flights %>%
    filter(carrier == "DL")
p <- ggplot(data = delta, aes(x = distance, y = air_time))
p + geom_point()
```

Longer distances have longer air times. The vertical bands are most likely
because some flights travel the same distance but have different air times.

# Activity 5
```{r}
jfk <- weather %>%
    filter(origin == "JFK" & month == 1 & day <= 15)
p <- ggplot(data = jfk, mapping = aes(x = time_hour, y = temp))
p + geom_line()
```

The graphs look similar to each other, although the JFK graph has higher and
lower peaks as compared to the Newark graph.

# Activity 6
```{r}
p <- ggplot(data = weather, aes(x = factor(month), y = wind_speed))
p + geom_boxplot() + ylim(0, 50)
```

# Activity 7
```{r}
def <- ggplot(data = weather, mapping = aes(x = wind_speed))
def + geom_histogram(color = "white") + xlim(0, 40)
wide <- ggplot(data = weather, mapping = aes(x = wind_speed))
wide + geom_histogram(bins = 10, color = "white") + xlim(0, 40)
narrow <- ggplot(data = weather, mapping = aes(x = wind_speed))
narrow + geom_histogram(bins = 50, color = "white") + xlim(0, 40)
```

The graph with the narrowest bins gives the best summary. The first graph with
auto-generated bin widths shows three peaks for wind speed: one at the very
beginning, another around 10, and right before 20. The graph with the widest
bin widths only shows one around 10. The graph with the narrowest bin widths
shows that the peak is a little before 10, but the closest surrounding points
are also very high.

# Activity 8
```{r}
p <- ggplot(data = flights, mapping = aes(x = origin, fill = carrier))
p + geom_bar(color = "white", position = position_dodge(preserve = "single"))
```

EWR: UA and EV, 
JFK: B6 and DL, 
LGA: DL and MQ