---
title: HW 3
author: Haley Uyeunten
output: html_document
---

```{r}
library(tidyverse)
library(gapminder)
library(nycflights13)
```

# Activity 2
```{r}
def <- ggplot(data = weather, mapping = aes(x = wind_speed))
def + geom_density(color = "darkblue", fill = "lightblue") + xlim(0, 40)
smooth <- ggplot(data = weather, mapping = aes(x = wind_speed))
smooth + geom_density(color = "darkblue", fill = "lightblue", bw = 5) + xlim(0, 40)
jagged <- ggplot(data = weather, mapping = aes(x = wind_speed))
jagged + geom_density(color = "darkblue", fill = "lightblue", bw = 0.5) + xlim(0, 40)
```

The graph with the default bandwidths in the most useful. It shows that there's
a peak at the very beginning, and then another a little before 10. The smooth
graph makes it look like the data has only one peak, and the jagged graph has
so many smaller peaks that it's difficult to understand easily.

# Activity 3
```{r}
p <- ggplot(data = weather, aes(x = factor(month), y = wind_speed))
p + geom_violin() + ylim(0, 50)
```

The violin plots show the distribution of the data points, when in the box 
plots, only the mean and interquartile range are easy to see. 