---
title: HW 4
author: Haley Uyeunten
output: html_document
---

```{r}
library(tidyverse)
library(gapminder)
library(nycflights13)
```

# Activity 1
```{r}
c <- gapminder %>% filter(country == "Canada")
p <- ggplot(data = c, mapping = aes(x = pop, y = gdpPercap))
p + geom_line()
p_time <- ggplot(data = c, mapping = aes(x = year, y = gdpPercap))
p_time + geom_line() + geom_point(mapping = aes(size = pop))
```

The second graph is better for comparing GDP and population over time. In the
first graph, time is implied, since it compares GDP to population. In the
second graph, time, GDP, and population are all visible at once, so it's easier
to compare them to each other.

# Activity 2
```{r}
d <- gapminder %>% filter(year == 2007)
p <- ggplot(data = d, mapping = aes(x = pop, y = gdpPercap, color = continent))
p + geom_point() + scale_x_log10()
```

No, there appears to be no relationship between population and GDP.

# Activity 3
```{r}
alaska_flights <- flights %>% filter(carrier == "AS")
p <- ggplot(data = alaska_flights, aes(x = dep_delay, y = arr_delay))
p + geom_point() + scale_x_log10()
```

The log of some points is not a number. If data has negative values, then
the log can't be taken.

# Activity 4
Why are many of the top NAICS codes 0?
How is the data sorted, or how should it be sorted?

# Activity 5
```{r}
d <- read.csv(file = "ABS_State_2017.csv")
c <- d %>% filter(NAME == "California")
p <- ggplot(data = c, mapping = aes(x = EMP, y = PAYANN, color = SECTOR))
p + geom_point() +
    scale_x_discrete(guide = guide_axis(check.overlap = TRUE)) +
    scale_y_discrete(guide = guide_axis(check.overlap = TRUE))
```